Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
fixed compile errors and added some conclusion (WIP)

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}
\usepackage{graphicx}

@@

    To more constrained settings, we also vary the cluster configuration and consider
    a memory-constrained cluster.
    Like the default cluster, it consists of 72 nodes (12 of each kind), but we
    give each node $10$ times less memory.
    So, the {\em luxury} machine $C2$ has $19.2$~GB memory in this setting instead of $192$~GB, $A2$ has $6.4$~\GB instead
    of $64$~GB etc.
    The processor speeds and their relations stay unchanged.

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{booktabs}

@@

    To more constrained settings, we also vary the cluster configuration and consider
    a memory-constrained cluster.
    Like the default cluster, it consists of 72 nodes (12 of each kind), but we
    give each node $10$ times less memory.
    So, the {\em luxury} machine $C2$ has $19.2$~GB memory in this setting instead of $192$~GB, $A2$ has $6.4$~GB instead
    of $64$~GB etc.
    The processor speeds and their relations stay unchanged.

@@

 \heftbl and \heftblc can schedule all workflows in a normal cluster and approximately a half of them in a memory-constrained
    one.
    They provide a runtime that scales well with the growing size of a workflow.

    \heftmm can schedule even the largest workflows even on the memory-constrained cluster.
    It is the only heuristic that had $100\%$ success rate.
    However, the makespans it produces are larger than those of the the other two
